%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
 
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ethan Leyden} \\ \vspace{1pt}
    \small 704-500-5351 $|$ \href{mailto:x@x.com}{\underline{etleyden@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/ethanleyden}{\underline{linkedin.com/in/ethanleyden}} $|$
    \href{https://github.com/etleyden}{\underline{github.com/etleyden}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Virginia Commonwealth University (VCU)}{Richmond, VA}
      {Bachelor of Science in Computer Science, Concentration in Data Science, GPA: 4.0}{Expected May 2025}
  \resumeSubHeadingListEnd


\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages}{: Python, Java, C/C++, MySQL, JavaScript/TypeScript, HTML/CSS, Common Lisp, Swift, PHP, Lua, LaTeX} \\
        \textbf{Frameworks}{: pandas, numpy, React, Node.js, Bootstrap, jQuery, p5.js/Processing} \\
        \textbf{Tools}{: pip, npm, git, Linux (Arch, Mint, Ubuntu), SLURM, Figma, Wordpress, JSON, XML, Vi/Vim/Neovim}
    }}  
    \end{itemize}
    

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{May 2024 -- Present}
      {VCU NanoNLP Lab}{Richmond, VA}
      \resumeItemListStart
        \resumeItem{Contributed to research about using large language models to generate synthetic training data for Named Entity Recognition (NER) systems.}
        \resumeItem{Expanded support of the project to utilize the Llama3 LLM for data generation.}
        \resumeItem{Wrote documentation, improving accessibility for future contributors.}
        \resumeItem{Performed preprocessing tasks on the CONLL2003 dataset, and adapted the system for other NER datasets.}
        \resumeItem{Used high performance computing systems to build and train ML models, scheduling jobs with SLURM.}
        \resumeItem{Delivered weekly presentations on some of the latest research in natural language processing.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {IT Analyst}{December 2023 -- November 2024}
      {Digital Neighbor}{Remote/Tampa, FL}
      \resumeItemListStart
        \resumeItem{Leveraging the latest SEO best practices to boost engagement on client websites.}
        \resumeItem{Implementing, updating, and monitoring client websites to be equipped with the necessary tools to track marketing leads.}
        \resumeItem{Troubleshooting issues on short-notice to ensure a seamless user-experience.}
    \resumeItemListEnd
    \resumeSubheading
      {Team Leader}{September 2020 -- Present}
      {Target T1931}{Richmond, VA}
      \resumeItemListStart
        \resumeItem{Demonstrate competent leadership for a team of 3-15 people, resulting in workload completion ahead of schedule.}
        \resumeItem{Proven track record of prioritizing the business needs, and as a result, gained a lot of business acumen.}
        \resumeItem{Oversaw various departments throughout the store, learning how to manage competing priorities in the best interest of the company.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{RVA Community Fridges Telemetry} $|$ \emph{LoRa, Meshtastic, Arduino/C++, git}}{}
        \resumeItemListStart
            \resumeItem{Designed a compact IoT solution with Raspberry Pi's to monitor refrigerator temperature and door usage.}
            \resumeItem{Leveraged USB cellular modems to transmit data from 15 community fridges in the Greater Richmond Area.}
            \resumeItem{Structured an Agile workflow as the Project Manager of a team of four people, conducting weekly sprints with mentorship from a faculty advisor. }
        \resumeItemListEnd
      \resumeProjectHeading
      {\textbf{NFL Prediction Model} $|$ \emph{Python, PostgreSQL, Scikit-learn, PyTorch, Pandas, git}}{}
        \resumeItemListStart
          \resumeItem{Independently designed a data pipeline that scrapes raw data from the internet, organizes it into a database, and subsequently compiles it into a CSV format for model training.}
          \resumeItem{Used scikit-learn and PyTorch to train models predicting the winner of NFL games with an accuracy as high as 
          58\%, outperforming amateur sports bettors.}
        \resumeItemListEnd
      \resumeProjectHeading
      {\textbf{React Color Picker} $|$ \emph{React, npm, HTML/CSS, Javascript/Typescript}}{}
          \resumeItemListStart
            \resumeItem{Designed and built a color picker tool using the React framework, demonstrating competency in the technologies used for front-end web development, as well as competency in UI/UX design. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%


%-------------------------------------------
\end{document}
